Federated Learning's Blessing: FedAvg has Linear Speedup

### 2021-06-27 source-TNNLS/main.tex
Update on Overleaf.
Add bio and reformat appendix

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
IEEE, IEEEtran, journal, \LaTeX, paper, template.
\end{IEEEkeywords}

@@

\input{sec_intro}
%\input{sec_relatedwork}
\input{sec_problem}
\input{sec_SGD}
\input{sec_Nesterov}
%\input{sec_overparameterized}
\input{sec_exp}

@@

@@

% use section* for acknowledgment
\section*{Acknowledgment}

@@

% if you will not have a photo at all:
\begin{IEEEbiographynophoto}{Kaixiang Lin}
Biography text here.
\end{IEEEbiographynophoto}

\begin{IEEEbiographynophoto}{Jane Doe}
Biography text here.
\end{IEEEbiographynophoto}

>>>>

% Note that keywords are not normally used for peerreview papers.
\begin{IEEEkeywords}
Federated learning, Optimization. 
\end{IEEEkeywords}

@@

\input{sec_intro}
%\input{sec_relatedwork}
\input{sec_problem}
\input{sec_SGD}
\input{sec_Nesterov}
%\input{sec_overparameterized}
\input{sec_exp}
\input{sec_conclude}

\input{sec_ack}

@@

\begin{comment}

% if you will not have a photo at all:
\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_kaixiang.png}}]{Kaixiang Lin}
Dr. Kaixiang Lin is an applied scientist at Amazon Lab 126. Before joining Amazon, 
Kaixiang received his Ph.D. degree in Computer Science at Michigan State University in 2020. 
\end{IEEEbiography}

\begin{IEEEbiography}[{\includegraphics[width=1in,height=1.25in,clip,keepaspectratio]{fig/bio_jiayu.png}}]{Jiayu Zhou}
Dr. Jiayu Zhou is an assistant professor at
 Department of Computer Science and Engineering, Michigan State University.
 Before joining MSU, Jiayu was a staff research scientist at Samsung Research
 America. Jiayu received his Ph.D. degree in computer science at Arizona
 State University in 2014. 
\end{IEEEbiography}

\end{comment}

@@

@@
